Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
sec2.3
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

% Straw man example
Migrating resources is an important part of load balancing but understanding the effects of different configurations and parameters is difficult. Systems already virtualize and migrate memory; soon systems will be able to migrate other resources, like CPU, disk, and memory. Figuring out how, when, and where to move these resources depends on complex metrics like utilization, configuration, and workload.

@@

\paragraph*{Malacology:}

For CephFS, designing a general POSIX metadata load balancer is difficult becuase the workloads are diverse and quickly changing. With CephFS, it is especially complicated because the system has variable sized migration units (i.e. file system namespace subtrees), which can be shipped anywhere (i.e., to any MDS of any capacity) at any time for any reason. Furthermore, the original balancer was designed with hard-coded policies and tunables. Both angles were difficult to understand. It is understandable why it was implemented this way -- it is difficult to pick a one-size-fits-all policy, system administrators may want to partition load based on SLAs, or applications are better equipped to make these decisions, etc. -- but we choose instead to expose a balancing API at strategic points in the balancing logic using Lua hooks.

\begin{figure}[htbp]
\centering
\includegraphics{figures/cls-osd-mds.png}
\caption{To generalize the LuaVM for use in both the OSD and MDS,
Malacology detaches the core functionality into a Lua core module. The
VM is dynamically loaded first (1) and then interfaces can execute (2).
\label{fig:cls-osd-mds}}
\end{figure}

@@

\subsection{File System Indexing and Locking}

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction. Distributed file systems are complex, but fundamentally
provide durable hierarchical indexing and distributed locking service.  The
locking service implements a capabilities that express what data and metadata
clients are allowed to access as well as what they may cache locally.  While
designed for a fixed file abstraction, indexing, locking, and caching are all
common services that are useful to large sets of applications.

\paragraph*{Malacology:} Malacogy adds interface hooks in strategic spots in the MDS to control the load balancing and capability subsystems.
Malacogy adds interface hooks in strategic spots in the MDS to control the load balancing and capability subsystems.

These hooks embed Lua code in the MDS using the
OSD subsystems. By re-using the OSD interface classes, the MDS gets the safety and robustness of loading dynamic code (including graceful failures and helpful errors), the ease of transferring state between object
interfaces and the OSD internals, integration with testing and
correctness suites, and \texttt{struct}s for interface data and
handlers.

The metadata service also manages sessions with its clients. This gives both subsystems (MDSs and clients) the ability cache data and grab locks. The metadata service is
responsible for responding to client requests for capabilities by first
revoking caps from other clients. Currently clients voluntarily
release their capabilities, and the MDS maintains a queue of requests.
Both clients and MDSs use a best-effort approach to revoking or releasing capabilities.

@@

>>>>

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction~\cite{cephfs}. Distributed file systems are complex, but
fundamentally provide hierarchical indexing and distributed locking services.
In Ceph, the locking service implements a capability-based system that express
what data and metadata clients are allowed to access as well as what state
they may cache and modify locally. While designed for a fixed file
abstraction, indexing, locking, and caching are all common services that are
useful to a broad spectrum of applications.

Ceph addresses the challenge of balancing load across the metadata cluster
using load balancing policies that compute balancing metrics based on system
state (e.g. CPU and memory utilization) and statistics collected by the
cluster (e.g. the popularity of an inode). Distributed applications that share
centralized resources (e.g. a database or directory) face similar challenges
which are often solved using application-specific sharding.

\paragraph*{Malacology:}
Malacogy adds interface hooks in strategic spots in the metadata service to
control load balancing, capability subsystems, and for defining new file
types allowing the indexing service to be repurposed for other types of
named resources.

{\bf Load balancing.}
For CephFS, designing a general POSIX metadata load balancer is difficult
becuase the workloads are diverse and quickly changing. With CephFS, it is
especially complicated because the system has variable sized migration units
(i.e. file system namespace subtrees), which can be shipped anywhere (i.e., to
any MDS of any capacity) at any time for any reason. Furthermore, the original
balancer was designed with hard-coded policies and tunables. Both angles were
difficult to understand. It is understandable why it was implemented this way
-- it is difficult to pick a one-size-fits-all policy, system administrators
may want to partition load based on SLAs, or applications are better equipped
to make these decisions, etc. -- but we choose instead to expose a balancing
API at strategic points in the balancing logic using Lua hooks.

@@

@@

{\bf Capabilities.}
The metadata service also manages sessions with its clients. This gives both
subsystems (MDSs and clients) the ability cache data and grab locks. The
metadata service is responsible for responding to client requests for
capabilities by first revoking caps from other clients. Currently clients
voluntarily release their capabilities, and the MDS maintains a queue of
requests.  Both clients and MDSs use a best-effort approach to revoking or
releasing capabilities.

@@

{\bf Policy management.} A new interface is added to the metadata service
subsystem using the monitoring framework to support management of interfaces,
which ensures durability and distribution of policies in a consistent way.

\begin{figure}[h]
\centering
\includegraphics{figures/cls-osd-mds.png}
\caption{To generalize the LuaVM for use in both the OSD and MDS,
Malacology detaches the core functionality into a Lua core module. The
VM is dynamically loaded first (1) and then interfaces can execute (2).
\label{fig:cls-osd-mds}}
\end{figure}

% Straw man example
%Migrating resources is an important part of load balancing but understanding
%the effects of different configurations and parameters is difficult. Systems
%already virtualize and migrate memory; soon systems will be able to migrate
%other resources, like CPU, disk, and memory. Figuring out how, when, and where
%to move these resources depends on complex metrics like utilization,
%configuration, and workload.

%These hooks embed Lua code in the MDS using the OSD subsystems. By re-using
%the OSD interface classes, the MDS gets the safety and robustness of loading
%dynamic code (including graceful failures and helpful errors), the ease of
%transferring state between object interfaces and the OSD internals,
%integration with testing and correctness suites, and \texttt{struct}s for
%interface data and handlers.
